Measurement and Probability in Fuzzy Quantum Theories

### 2017-01-18 prop.tex
prop.tex \newcommand{\set}[2] Added...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}

@@

The conventional definition of a probability space builds upon the
field of real numbers. In more detail, a probability space consists of
a \emph{sample space} $\Omega$, a space of \emph{events}~$\events$,
and a \emph{probability measure}~$\pmeas$ mapping events in $\events$
to the real interval $[0,1]$. We will only consider \emph{finite} sets
of events and restrict our attention to non-empty finite sets $\Omega$
as the sample space. The space of events $\events$ includes every
possible subset of $\Omega$: it is the
powerset~$2^{\Omega}=\left\{ E ~\middle|~ E\subseteq\Omega\right\}
$.
For future reference, we emphasize that events are the primary notion
of interest and that the sample space is a convenient artifact that
allows us to treat events as sets obeying the laws of Boolean
algebra~\cite{Boole1948,Redhead1987-REDINA,Griffiths2003}.

@@

In general, we conjecture that if the measurement equipment is made
more and more precise, the corresponding interval-valued probability
measure will be closer and closer to the Born rule. In the limit case,
$\mathscr{I}=\left\{ \left\{ a\right\}
  ~\middle|~a\in\left[0,1\right]\right\}$
we do indeed recover the conventional Gleason's theorem and the Born
rule.

@@

In example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
although quantum IVPMs have empty cores, we might think that the probability
measure~$\bar{\mu}$ is induced by some states. In example~\ref{ex:three-dimensional-three-value},
the probability measure $\bar{\mu}$ might be induced by the state
$\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
or induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$.
In example~\ref{ex:three-dimensional-4-value}, the probability measure
$\bar{\mu}$ might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
Notice that the set of 1-dimensional projectors mapping to impossible,
$\bar{\mu}^{-1}\left(\imposs\right)=\left\{ \ket{\psi}\in\mathbb{C}^{3}~\middle|~\bar{\mu}(\proj{\psi})=\imposs\right\} $
provides a appealing way to suggest a possible state inducing $\bar{\mu}$.
Since for any two states~$\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\bar{\mu}^{-1}\left(\imposs\right)$,
we have $\bar{\mu}(\proj{\psi_{0}})=\bar{\mu}(\proj{\psi_{1}})=\imposs$
so that $\bar{\mu}$ might be induced by the state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$\footnote{\yutsung{Just notice that I only focus on $\mathbb{R}^{3}$ instead
of $\mathbb{C}^{3}$. Although this might be just tedious details
in this approach, still need to verify carefully.}}. Notice that even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are
normalized, when they are not orthogonal, $\ket{\psi_{0}}\times\ket{\psi_{1}}$
is not normalized. We will use $\ket{\psi_{0}}\times\ket{\psi_{1}}$
and the normalized $\ket{\psi_{0}}\times\ket{\psi_{1}}$ interchanged
when there is no confusion. There are 4 different cases.
\begin{enumerate}
\item If another pair of states~$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{\mu}^{-1}\left(\imposs\right)$
gives different state of cross product~$\ket{\psi_{0}'}\times\ket{\psi_{1}'}$,
then both $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
might induce $\bar{\mu}$, but neither $\mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$
nor $\mu_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ in the core
of $\bar{\mu}$. Actually, $\bar{\mu}$ has an empty core. 
\item If $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
always represent the same state for all $\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{\mu}^{-1}\left(\imposs\right)$,
then $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is the only pure state
which might induce $\bar{\mu}$. In another word, if $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$
for some pure state~$\ket{\phi}$, then $\ket{\phi}$ and $\ket{\psi_{0}}\times\ket{\psi_{1}}$
represent the same state. 
\item $\bar{\mu}^{-1}\left(\imposs\right)$ may contain only one state~$\ket{\psi_{0}}$.
In this case, $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is undefined.
If $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$ for some
pure state~$\ket{\phi}$, $\ket{\phi}$ could be any state orthogonal
to $\ket{\psi_{0}}$.
\item $\bar{\mu}^{-1}\left(\imposs\right)=\emptyset$. If $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$
for some pure state~$\ket{\phi}$, we could say nothing about $\ket{\phi}$.
\end{enumerate}
In summary, if we have an idea of $\bar{\mu}^{-1}\left(\imposs\right)$,
we could have some idea of the pure states which are in core.

@@

\section{Subset of Computing Events}

@@

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}

@@

The conventional definition of a probability space builds upon the
field of real numbers. In more detail, a probability space consists
of a \emph{sample space} $\Omega$, a space of \emph{events}~$\events$,
and a \emph{probability measure}~$\pmeas$ mapping events in $\events$
to the real interval $[0,1]$. We will only consider \emph{finite}
sets of events and restrict our attention to non-empty finite sets
$\Omega$ as the sample space. The space of events $\events$ includes
every possible subset of $\Omega$: it is the powerset~$2^{\Omega}=\set{E}{E\subseteq\Omega}$.
For future reference, we emphasize that events are the primary notion
of interest and that the sample space is a convenient artifact that
allows us to treat events as sets obeying the laws of Boolean algebra~\cite{Boole1948,Redhead1987-REDINA,Griffiths2003}.

@@

In general, we conjecture that if the measurement equipment is made
more and more precise, the corresponding interval-valued probability
measure will be closer and closer to the Born rule. In the limit case,
$\mathscr{I}=\set{\left\{ a\right\} }{a\in\left[0,1\right]}$ we do
indeed recover the conventional Gleason's theorem and the Born rule.

@@

In example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
although quantum IVPMs have empty cores, we might think that the probability
measure~$\bar{\mu}$ is induced by some states. In example~\ref{ex:three-dimensional-three-value},
the probability measure $\bar{\mu}$ might be induced by the state
$\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
or induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$.
In example~\ref{ex:three-dimensional-4-value}, the probability measure
$\bar{\mu}$ might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
Notice that the set of 1-dimensional projectors mapping to impossible,
$\bar{\mu}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}^{3}}{\bar{\mu}(\proj{\psi})=\imposs}$
provides a appealing way to suggest a possible state inducing $\bar{\mu}$.
Since for any two states~$\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\bar{\mu}^{-1}\left(\imposs\right)$,
we have $\bar{\mu}(\proj{\psi_{0}})=\bar{\mu}(\proj{\psi_{1}})=\imposs$
so that $\bar{\mu}$ might be induced by the state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$\footnote{\yutsung{Just notice that I only focus on $\mathbb{R}^{3}$ instead
of $\mathbb{C}^{3}$. Although this might be just tedious details
in this approach, still need to verify carefully.}}. Notice that even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are
normalized, when they are not orthogonal, $\ket{\psi_{0}}\times\ket{\psi_{1}}$
is not normalized. We will use $\ket{\psi_{0}}\times\ket{\psi_{1}}$
and the normalized $\ket{\psi_{0}}\times\ket{\psi_{1}}$ interchanged
when there is no confusion. There are 4 different cases.
\begin{enumerate}
\item If another pair of states~$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{\mu}^{-1}\left(\imposs\right)$
gives different state of cross product~$\ket{\psi_{0}'}\times\ket{\psi_{1}'}$,
then both $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
might induce $\bar{\mu}$, but neither $\mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$
nor $\mu_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ in the core
of $\bar{\mu}$. Actually, $\bar{\mu}$ has an empty core. 
\item If $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
always represent the same state for all $\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{\mu}^{-1}\left(\imposs\right)$,
then $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is the only pure state
which might induce $\bar{\mu}$. In another word, if $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$
for some pure state~$\ket{\phi}$, then $\ket{\phi}$ and $\ket{\psi_{0}}\times\ket{\psi_{1}}$
represent the same state. 
\item $\bar{\mu}^{-1}\left(\imposs\right)$ may contain only one state~$\ket{\psi_{0}}$.
In this case, $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is undefined.
If $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$ for some
pure state~$\ket{\phi}$, $\ket{\phi}$ could be any state orthogonal
to $\ket{\psi_{0}}$.
\item $\bar{\mu}^{-1}\left(\imposs\right)=\emptyset$. If $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$
for some pure state~$\ket{\phi}$, we could say nothing about $\ket{\phi}$.
\end{enumerate}
In summary, if we have an idea of $\bar{\mu}^{-1}\left(\imposs\right)$,
we could have some idea of the pure states which are in core.

@@

\section{Subset of Commuting Events}

@@

Given an orthonormal basis~$\mathcal{B}=\left\{ \ket{\psi_{1}},\ldots,\ket{\psi_{d}}\right\} $
of a Hilbert space, the set of projections generated by the basis
is $\events'=\set{\sum_{\ket{\psi}\in S}\ket{\psi}}{S\subseteq\mathcal{B}}$.
Because $\left(2^{\mathcal{B}},\emptyset,\mathcal{B},\cup,\cap\right)$
is isomorphic to $\left(\events',\mathbb{0},\mathbb{1},\vee,\cdot\right)$
as a Boolean algebra, a quantum IVPM~$\bar{\mu}':\events'\rightarrow\mathscr{I}$
is essentially a classical IVPM~$\bar{\mu}:2^{\mathcal{B}}\rightarrow\mathscr{I}$.
By the Shapley theorem, if $\bar{\mu}'$ is convex, it should have
a non-empty core.

The problem is: if $\events'$ is only a commuting subset of $\events$,
does a convex quantum IVPM~$\bar{\mu}':\events'\rightarrow\mathscr{I}$
always has a non-empty core?
